---
title: "MI/Stroke Inpatient"
format: html
  # docx:
  #   fig-cap-location: top
execute:
  echo: false
  message: false
  warning: false
lof: true
---

```{r}
# Load necessary packages ----
library(OmopSketch)
library(visOmopResults)

# Load results stored in the package ----
fileData <- file.path(getwd(), "data", "studyData.RData")
if (!file.exists(fileData)) {
  source(file.path(getwd(), "rawData", "preprocess.R"))
}

# uncomment to load the raw data
# rawData <- omopgenerics::importSummarisedResult(file.path(getwd(), "rawData"))

# load data
load(fileData)

# source functions
source(file.path(getwd(), "functions.R"))

# Global options ----
knitr::opts_chunk$set(
  out.width  = "95%",  # figures occupy ~95% of document width
  out.height = "auto",
  dpi        = 320,    # ensure figure quality
  fig.width  = 6,      # default aspect ratio (can be overridden per-figure)
  fig.height = 3,
  results    = "asis"  # enable Markdown produced via cat() inside chunks
)

setGlobalPlotOptions(type = "ggplot")
setGlobalTableOptions(type = "flextable")
tt <- "flextable"
```

## Database metadata

:::{custom-style="Caption"}
**Table 1:** Database metadata.
:::

```{r}
OmopSketch::tableOmopSnapshot(data[["summarise_omop_snapshot"]], type = tt)
```

## Demographics characterisation MI

:::{custom-style="Caption"}
**Table 2:** Demographics characterisation at first record of Myocardial infarction.
:::

```{r}
arrangeCharacteristics <- function(x) {
  x |>
    dplyr::mutate(order_id = dplyr::case_when(
      variable_name == "Number records" ~ 1L,
      variable_name == "Number subjects" ~ 2L,
      variable_name == "Cohort start date" ~ 3L,
      variable_name == "Sex" ~ 5L,
      variable_name == "Age" ~ 6L,
      variable_name == "Age group" ~ 7L,
      variable_name == "Ethnicity" ~ 8L,
      variable_name == "SES" ~ 9L,
      variable_name == "Prior observation" ~ 10L,
      variable_name == "Future observation" ~ 11L,
      variable_name == "MI type" ~ 12L,
      variable_name == "28-day mortality" ~ 13L,
      variable_name == "Prior comorbidities (-inf to 0)" ~ 14L
    )) |>
    dplyr::arrange(order_id, variable_level) |>
    dplyr::select(!"order_id")
}
data$summarise_demographics |>
  arrangeCharacteristics() |>
  omopgenerics::filterGroup(cohort_name == "AMI") |>
  omopgenerics::filterStrata(strata == "overall") |>
  CohortCharacteristics::tableCharacteristics(
    hide = c("strata", "cohort_name", "table_name", "age_range", "ses", "sex", "mi_type"),
    header = c("cdm_name"),
    type = tt
  )
```

### AMI by type

```{r}
data$summarise_demographics |>
  arrangeCharacteristics() |>
  omopgenerics::filterGroup(cohort_name == "AMI") |>
  omopgenerics::filterStrata(mi_type != "overall") |>
  CohortCharacteristics::tableCharacteristics(
    hide = c("strata", "cohort_name", "table_name", "age_range", "ses", "sex"),
    header = c("cdm_name", "mi_type"),
    type = tt
  )
```

### Compare sex MI

```{r, results='asis'}
data$summarise_demographics |>
  arrangeCharacteristics() |>
  omopgenerics::filterGroup(cohort_name == "AMI") |>
  omopgenerics::filterStrata(sex != "overall") |>
  CohortCharacteristics::tableCharacteristics(
    hide = c("strata", "cohort_name", "table_name", "age_range", "ses", "mi_type"),
    header = c("cdm_name", "sex"),
    type = tt
  )
```

## Stroke

```{r}
data$summarise_demographics |>
  arrangeCharacteristics() |>
  omopgenerics::filterGroup(grepl("AIS", cohort_name)) |>
  omopgenerics::filterStrata(strata == "overall") |>
  CohortCharacteristics::tableCharacteristics(
    hide = c("strata", "table_name", "age_range", "ses", "sex", "mi_type"),
    header = c("cdm_name", "cohort_name"),
    type = tt
  )
```


### RESULTS (ABM)

##Supplementary Table 1: Features of each hospital 

##Table 1: General description of the populations: AIS and AMI counts and sociodemographic and comorbidities (for AIS and AMI)


##Table 2: the pattern of use of medications (antiplatelets, anticoagulants, statins, thrombolytics) (for AIS and AMI)across centres

```{r, fig.height=10}
x <- data$summarise_treatments |>
  omopgenerics::tidy() |>
  dplyr::filter(
    !grepl("Beta blocker ", variable_level),
    !grepl("Acei arbs ", variable_level),
    !grepl("Calcium channel blocker ", variable_level),
    !grepl("Thrombin inhibitors ", variable_level),
    !grepl("Thiazide ", variable_level),
    !grepl("Pcsk9", variable_level)
  ) |>
  dplyr::arrange(variable_level)
ggplot2::ggplot(data = x, mapping = ggplot2::aes(x = variable_level, y = percentage, fill = variable_level)) +
  ggplot2::geom_col() +
  ggplot2::coord_flip() +
  ggplot2::facet_grid(cohort_name ~ cdm_name) +
  ggplot2::theme(legend.position = "none")
```


	MI and AIS: statins use
	AIS-AF: DOAC, warfarin 


### Table 3: the patterns of use of procedures (PCI, storke_procedures_rx (EVT, intra and extracranial stenting))

##Table 4: timing to reperfussion treatment (admission>>thrombolytics, admission>PCI/stroke_procedures_rx) (Lancshire). 
#Figure 1: differences for age
#Figure 2: differences for SES

##Figure 3 and 4: statins use (for AIS and AMI): differences for sex and age

## Statin

```{r, fig.height=10}
xs <- x |>
  dplyr::filter(variable_level == "Statin") |>
  dplyr::mutate(
    strata_group = stringr::str_extract(strata, "^[^:]+")
  )
ggplot2::ggplot(data = xs, mapping = ggplot2::aes(x = strata, y = percentage, fill = strata_group)) +
  ggplot2::geom_col() +
  ggplot2::coord_flip() +
  ggplot2::facet_grid(cohort_name ~ cdm_name) +
  ggplot2::theme(legend.position = "none")
```

## P2y12 inhibitors ticagrelor

```{r, fig.height=10}
xs <- x |>
  dplyr::filter(variable_level == "P2y12 inhibitors ticagrelor") |>
  dplyr::mutate(
    strata_group = stringr::str_extract(strata, "^[^:]+")
  )
ggplot2::ggplot(data = xs, mapping = ggplot2::aes(x = strata, y = percentage, fill = strata_group)) +
  ggplot2::geom_col() +
  ggplot2::coord_flip() +
  ggplot2::facet_grid(cohort_name ~ cdm_name) +
  ggplot2::theme(legend.position = "none")
```
##Figure 5 and 6: Ticagrelor vs clopidogrel (for AIS and AMI): differences for sex and age

# ```{r, fig.height=10}
# xs <- x |>
#   dplyr::filter(variable_level %in% c("P2y12 inhibitors ticagrelor", "P2y12 inhibitors clopidogrel")) |>
#   dplyr::mutate(
#     strata_group = stringr::str_extract(strata, "^[^:]+")
#   )
# ggplot2::ggplot(data = xs, mapping = ggplot2::aes(x = strata, y = percentage, fill = strata_group)) +
#   ggplot2::geom_col() +
#   ggplot2::coord_flip() +
#   ggplot2::facet_grid(cohort_name ~ cdm_name) +
#   ggplot2::theme(legend.position = "none")
# ```

```{r}
x <- data$summarise_procedures |>
  omopgenerics::tidy() |>
  dplyr::filter(strata == "overall") |>
  dplyr::arrange(variable_level)
ggplot2::ggplot(data = x, mapping = ggplot2::aes(x = variable_level, y = percentage, fill = variable_level)) +
  ggplot2::geom_col() +
  ggplot2::coord_flip() +
  ggplot2::facet_grid(cohort_name ~ cdm_name) +
  ggplot2::theme(legend.position = "none")
```



##Figure 7 and 8 (AIS-AF): Anticoagulants use (DOAC vs warfarin): differences for sex and age

##Table 5: Outcomes (for AIS and AMI)>> discharge destination and death
